Rapid cycleway prioritisation tool

### 2020-06-05 code/index.Rmd
Fix typo on landing page
Fix another typo in index

The [rapid cycleway prioritisation tool](https://www.cyipt.bike/rapid/) helps identify promising locations for road space reallocation in England to create new cycleways.
Used with local knowledge, it provides a strong evidence base to support planning of rapid measures to support safe travel as part of the COVID-19 response.
The rational for the tool is that, in the context of COVID-19, big decisions need to be made quickly.
The tool aims to support fast yet informed decision making a 'first pass' to help focus planning attention on road sections that are most likely to be suitable for new schemes.

@@

## 3. Spare lane(s) (not shown by default)

@@

## 4. Width >= 10m (not shown by default)

>>>>

The [rapid cycleway prioritisation tool](https://www.cyipt.bike/rapid/) helps identify promising locations for road space reallocation in England to create new cycleways.
Used with local knowledge, it provides an evidence base to support planning of rapid measures to support safe travel as part of the COVID-19 response.
The rational for the tool is that, in the context of COVID-19, big decisions need to be made quickly.
The tool aims to support fast yet informed decision making, by providing a 'first pass' assessment of the existing road network to help focus planning attention on options that are likely to have sufficient space for new infrastructure in places where there is high latent demand.

@@

## 4. Spare lane(s) (not shown by default)

@@

## 5. Width >= 10m (not shown by default)
